Smooth risk-based predictive approaches to treatment effect heterogeneity: A simulation study

### 2021-06-15 submission/manuscript.rmd
proof reading sections

We used the risk linear predictor to fit the the proposed methods under study
for individualizing absolute benefit predictions. All methods had quite
comparable results, in the sense that we predicted increasing benefits for
patients with higher baseline risk predictions. In terms of c-for benefit,
validated internally, all models had quite comparable performance ranging from
0.519 (RCS smoothing with 3 knots) to 0.542 (RCS smoothing with 4 knots).
Similar conclusions could be drawn in terms of ICI-for-benefit which ranged
from 0.0039 (linear interaction approach) to 0.0053 (RCS smoothing with 4
knots).

>>>>

We used the risk linear predictor to fit the the proposed methods under study
for individualizing absolute benefit predictions. All methods had quite
comparable results, in the sense that we predicted increasing benefits for
patients with higher baseline risk predictions. In terms of c-for benefit 
(validated internally) all models had quite comparable performance ranging from
0.519 (RCS smoothing with 3 knots) to 0.542 (RCS smoothing with 4 knots).
Similar conclusions could be drawn in terms of ICI-for-benefit which ranged
from 0.0039 (linear interaction approach) to 0.0053 (RCS smoothing with 4
knots).
